---
title: "grc-ueas26-poster"
author: "Tiffany Paalman"
date: 07/01/2026
toc: true
format: 
  revealjs: default
  html:
    df-print: paged
    code-fold: true
    code-tools: true
editor: visual
editor_options: 
  chunk_output_type: console
---

## GRC: Unifying Ecology Across Scales Poster

July 11 - 17, 2026

Stonehill College, Easton, MA

#### Pits & Pieces: Investigating the relative effects of habitat degradation and food web alteration on ecosystem structure, function, and recovery

#### Abstract:

It is well established that habitat degradation and food web alteration can individually drive loss of ecosystem structure and function. How these two forces can interact has received less attention. Theory predicts that loss of habitat can decrease top-down forcing in a system if the range of keystone consumers is limited to that habitat and increase it if the consumers are highly mobile with a range well beyond the area of degraded ecosystem. Experimental tests of this theory are uncommon. We experimentally tested the latter prediction in oyster reef systems, which have experienced widespread anthropogenic degradation over the past century. Concomitant with this degradation has been overlapping food web alteration in the wider seascape, with loss of top predators potentially leading to increases in mesopredator ray populations. Rays forage around and within reef systems, excavating adjacent sediments in search of invertebrates to create “pits”. These feeding disturbances can dislodge and bury oysters on the edge of patches – an effect that should increase within increasing edge to area ratio of a degraded reef. We expect that the suppression of oyster recovery is increased synergistically by a high degree of habitat degradation and high ray foraging activity. Here, I present preliminary data combining experimental manipulations of ray foraging and degree of degradation and combining regional surveys using UAS imagery across a 10-year time scale to investigate 1) how oyster reef structural characteristics vary with ray foraging intensities over time and 2) the relative effect of ray foraging and oyster cover (as a proxy for degradation) on oyster reef recovery, structure, and function.

## Experimental Data Analysis

### Data Loading & Tidying

```{r}
#| label: load-packages
#| include: false
#| message: false

library(tidyverse)
library(ggplot2)
library(car)
library(broom)
library(patchwork)
library(here)
library(readxl)
library(performance)
library(glmmTMB)
library(dplyr)
```

```{r}
#| label: load-spring2026-data
#| include: false
#| message: false

spr26_d_oys <- read_excel(here::here("data", "raw", "20260516_imagery_data_analysis", "c20260516_oys_data.xlsx"))
spr26_d_pits <- read_excel(here::here("data", "raw", "20260516_imagery_data_analysis", "c20260516_pits_data.xlsx"))
spr26_f_oys <- read_excel(here::here("data", "processed", "spr26_field_oyster.xlsx"))
spr26_f_reef <- read_excel(here::here("data", "processed", "spr26_field_reef.xlsx"))
treatments <- read_excel(here::here("data", "processed", "treatments.xlsx"))

glimpse(spr26_d_oys)
glimpse(spr26_d_pits)
glimpse(spr26_f_oys)
glimpse(spr26_f_reef)
glimpse(treatments)
```

```{r}
#| label: clean-drone-data
#| include: false
#| message: false

#clean drone oyster data
spr26_d_oys <- spr26_d_oys %>%
  dplyr::select(
    plot = `c20260516_oys_data.plot`,
    oys_area = `c20260516_oys_data.SUM_oys_area`,
    oys_perimeter = `c20260516_oys_data.SUM_oys_perim`,
    treated_oys_perc_cover = `c20260516_oys_data.treated_oys_perc_cover`,
    treatment = `20260516_plotpolygon.treatment`,
    plot_area = `20260516_plotpolygon.plot_area`
  ) %>%
  mutate(plot = as.numeric(plot))

#clean drone pit data
spr26_d_pits <- spr26_d_pits %>%
  dplyr::select(
    plot = `c20260516_pits_data.plot`,
    pit_area = `c20260516_pits_data.SUM_pit_area`,
    pit_count = `c20260516_pits_data.COUNT_pit_area`,
    pit_cover_percent = `c20260516_pits_data.pit_cover_perc`,
    treatment = `20260516_plotpolygon.treatment`
  ) %>%
  mutate(plot = as.numeric(plot))

#parse treatment information (extract cover % and ray access)
treatments <- treatments %>%
  dplyr::mutate(
    cover_level = as.factor(treatment__cover_percent),
    ray_access = factor(ray_access, levels = c("caged", "control"))
  ) %>%
  dplyr::select(plot, cover_level, ray_access, treatment_long)

#merge all plot level data
exp_data <- spr26_d_oys %>%
  full_join(spr26_d_pits, by = c("plot", "treatment")) %>%
  left_join(treatments, by = "plot") %>%
  dplyr::select(plot, cover_level, ray_access, everything())

#write csv
write.csv(exp_data, "~/Library/CloudStorage/OneDrive-Personal/projects/github/grc-ueas26-poster/data/processed/exp_data.csv")

#remove duplicates
exp_data <- read_csv(here::here("data", "processed", "exp_data.csv")) %>%
  distinct(plot, .keep_all = TRUE)

# verify
nrow(exp_data)  # Should be 64
n_distinct(exp_data$plot)  # Should be 64

#check for missing data
print(colSums(is.na(exp_data)))

print(head(exp_data, 10))
```

```{r}
#| label: load-sum25-data
#| include: false
#| message: false

sum25_f_oys <- read_excel(here::here("data", "processed", "sum25_field_oyster.xlsx"))
sum25_f_reef <- read_excel(here::here("data", "processed", "sum25_field_reef_structure.xlsx"))
```

```{r}
#| label: clean-field-data
#| include: false
#| message: false

#2025 data
sum25_f_oys <- sum25_f_oys %>%
  dplyr::filter(!is.na(live_oyster_count) & !is.na(dead_oyster_count)) %>%
  dplyr::select(
    plot,
    live_count_initial = live_oyster_count,
    dead_count_initial = dead_oyster_count,
    spat_count_initial = spat_count,
    starts_with("oyster_length")
  ) %>%
  dplyr::mutate(plot = as.numeric(plot),
                across(starts_with("oyster_length"), as.numeric)) %>%
  group_by(plot) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    total_oyster_initial = live_count_initial + dead_count_initial,
    percent_live_initial = (live_count_initial / total_oyster_initial) * 100
  ) %>%
  rowwise() %>%
  mutate(
    mean_oyster_length_initial = mean(c_across(starts_with("oyster_length")), na.rm = TRUE)
  ) %>%
  ungroup() %>%
  dplyr::select(plot, live_count_initial, dead_count_initial, spat_count_initial, 
                percent_live_initial, mean_oyster_length_initial)

sum25_f_reef <- sum25_f_reef %>%
  dplyr::select(
    plot,
    clump_count,
    perc_cover,
    highest_height_cm,
    random_height_1_cm,
    random_height_2_cm,
    random_height_3_cm
  ) %>%
  dplyr::mutate(
    plot = as.numeric(plot),
    mean_height = rowMeans(dplyr::select(., ends_with("_cm")), na.rm = TRUE)
  ) %>%
  group_by(plot) %>%
  summarise(
    mean_clump_count_initial = mean(clump_count, na.rm = TRUE),
    mean_perc_cover_initial = mean(perc_cover, na.rm = TRUE),
    mean_height_initial = mean(mean_height, na.rm = TRUE),
    .groups = 'drop'
  )


#2026 data
spr26_f_oys <- spr26_f_oys %>%
  #filter out rows with missing live/dead counts
  dplyr::filter(!is.na(live_oyster_count) & !is.na(dead_oyster_count)) %>%
  dplyr::select(
    plot,
    quad,
    live_count = live_oyster_count,
    dead_count = dead_oyster_count,
    spat_count = spat_count,
    starts_with("oyster_length")
  ) %>%
  mutate(plot = as.numeric(plot)) %>%
  #group by plot and take the first non-NA record per plot
  group_by(plot) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    total_oyster_count = live_count + dead_count,
    percent_live = (live_count / total_oyster_count) * 100
  ) %>%
  mutate(
    mean_oyster_length = rowMeans(
      dplyr::select(., starts_with("oyster_length")), na.rm = TRUE
    )
  ) %>%
  dplyr::select(plot, live_count, dead_count, spat_count, percent_live, mean_oyster_length)

spr26_f_reef <- spr26_f_reef %>%
  dplyr::select(
    plot,
    quad,
    clump_count,
    perc_cover,
    highest_height_cm,
    random_height_1_cm,
    random_height_2_cm,
    random_height_3_cm
  ) %>%
  mutate(
    plot = as.numeric(plot),
    mean_height = rowMeans(
      dplyr::select(., ends_with("_cm")), na.rm = TRUE
    )
  ) %>%
  group_by(plot) %>%
  summarise(
    mean_clump_count = mean(clump_count, na.rm = TRUE),
    mean_perc_cover = mean(perc_cover, na.rm = TRUE),
    mean_highest_height = mean(highest_height_cm, na.rm = TRUE),
    mean_height_all = mean(mean_height, na.rm = TRUE),
    .groups = 'drop'
  )
```

```{r}
#| label: join-data
#| include: false
#| message: false

#join field data to experiment data with summer 2025 baseline
exp_data_full <- exp_data %>%
  left_join(spr26_f_reef, by = "plot") %>%
  left_join(spr26_f_oys, by = "plot") %>%
  # Join initial baseline data (July 2025)
  left_join(sum25_f_reef, by = "plot") %>%
  left_join(sum25_f_oys, by = "plot")

#screen for duplicates
duplicate_count <- exp_data_full %>%
  group_by(plot) %>%
  summarise(n = n(), .groups = 'drop') %>%
  filter(n > 1)

#remove duplicates and add change variables
exp_data_full <- exp_data_full %>%
  distinct(plot, .keep_all = TRUE) %>%
  #change over time(delta)
  mutate(
    delta_live_oysters = live_count - live_count_initial,
    delta_dead_oysters = dead_count - dead_count_initial,
    delta_spat = spat_count - spat_count_initial,
    delta_percent_live = percent_live - percent_live_initial,
    delta_reef_height = mean_height_all - mean_height_initial,
    delta_clump_count = mean_clump_count - mean_clump_count_initial,
    initial_cover_level = as.numeric(as.character(cover_level)),
    delta_oyster_cover = treated_oys_perc_cover - initial_cover_level,
    whole_oys_perc_cover = (oys_area / plot_area) * 100,
    pit_count = replace_na(pit_count, 0),
    pit_cover_percent = replace_na(pit_cover_percent, 0),
    relative_delta_oyster_cover = delta_oyster_cover / initial_cover_level
  )
```

### Summary statistics for UAV imagery

```{r}
#| label: spr26-drone-summary-stats

oyster_summary <- exp_data_full %>%
  group_by(cover_level, ray_access) %>%
  summarise(
    n = n(),
    mean_cover = mean(treated_oys_perc_cover, na.rm = TRUE),
    sd_cover = sd(treated_oys_perc_cover, na.rm = TRUE),
    se_cover = sd_cover / sqrt(n),
    .groups = 'drop'
  ) %>%
  arrange(cover_level, ray_access)
print(oyster_summary)

pit_summary <- exp_data_full %>%
  group_by(cover_level, ray_access) %>%
  mutate(
    pit_count = replace_na(pit_count, 0),
    pit_cover_percent = replace_na(pit_cover_percent, 0)
  ) %>% 
  summarise(
    n = n(),
    mean_pit_count = mean(pit_count, na.rm = TRUE),
    sd_pit_count = sd(pit_count, na.rm = TRUE),
    se_pit_count = sd_pit_count / sqrt(n),
    mean_pit_cover = mean(pit_cover_percent, na.rm = TRUE),
    sd_pit_cover = sd(pit_cover_percent, na.rm = TRUE),
    se_pit_cover = sd_pit_cover / sqrt(n),
    .groups = 'drop'
  )
print(pit_summary)
```

### Summary statistics for field data

```{r}
#| label: spr26-field-summary

field_summary <- exp_data_full %>%
  group_by(cover_level, ray_access) %>%
  summarise(
    mean_live_oysters = mean(live_count, na.rm = TRUE),
    se_live_oysters = sd(live_count, na.rm = TRUE) / sqrt(n()),
    mean_dead_oysters = mean(dead_count, na.rm = TRUE),
    se_dead_oysters = sd(dead_count, na.rm = TRUE) / sqrt(n()),
    mean_spat = mean(spat_count, na.rm = TRUE),
    se_spat = sd(spat_count, na.rm = TRUE) / sqrt(n()),
    mean_clump = mean(mean_clump_count, na.rm = TRUE),
    se_clump = sd(mean_clump_count, na.rm = TRUE) / sqrt(n()),
    mean_reef_height = mean(mean_height_all, na.rm = TRUE),
    se_reef_height = sd(mean_height_all, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )
print(field_summary)
```

### Statistics + Figures

#### Oyster Cover Change

```{r}
#| label: fig-themes
#| include: false
#| message: false

theme_set(theme_bw(base_size = 12) +
            theme(
              panel.grid.minor = element_blank(),
              legend.position = "bottom",
              plot.title = element_text(hjust = 0.5, face = "bold", size = 13),
              strip.text = element_text(face = "bold")
            ))
```

```{r}
#| label: final-oyster-fig

# oyster change cover anova
anova_recovery <- aov(delta_oyster_cover ~ cover_level * ray_access, data = exp_data_full)
print(summary(anova_recovery))

#check assumptions
plot(anova_recovery)


# figure colors
colors_treatment <- c(
  "25-Exclusion"    = "#A8D5E2",
  "25-Open"     = "#007A87",
  "50-Exclusion"    = "#CFE39A",
  "50-Open"     = "#6B8E23",
  "75-Exclusion"    = "#F4B39D",
  "75-Open"     = "#D24A33",
  "100-Exclusion"   = "#D4C2F0",
  "100-Open"    = "#5A3E99"
)

# prep data
cover_change_summary <- exp_data_full %>%
  group_by(cover_level, ray_access) %>%
  summarise(
    n = n(),
    mean_change = mean(delta_oyster_cover, na.rm = TRUE),
    sd_change = sd(delta_oyster_cover, na.rm = TRUE),
    se_change = sd_change / sqrt(n),
    .groups = 'drop'
  ) %>%
  mutate(
    ray_type = factor(ifelse(ray_access == "caged", "Exclusion", "Open"),
                      levels = c("Exclusion", "Open")),
    cover_level = factor(
      cover_level,
      levels = c("25", "50", "75", "100")
    ),
    color_key = paste0(cover_level, "-", ray_type)
  )

# plot
cover_change_fig <- ggplot(
  cover_change_summary,
  aes(x = ray_type, y = mean_change, fill = color_key)
) +
  geom_col(color = "black", width = 0.6, linewidth = 0.8) +
  geom_errorbar(
    aes(ymin = mean_change - se_change, ymax = mean_change + se_change),
    width = 0.3, 
    color = "black", 
    linewidth = 0.9
  ) +
  geom_hline(
    yintercept = 0, 
    linetype = "dashed", 
    color = "gray60", 
    linewidth = 0.7
  ) +
  facet_wrap(
    ~ cover_level, 
    nrow = 1,
    labeller = labeller(
      cover_level = c(
        "25" = "Initial 25% Cover",
        "50" = "Initial 50% Cover",
        "75" = "Initial 75% Cover",
        "100" = "Initial 100% Cover"
      )
    )
  ) +
  labs(
    x = "",
    y = "Absolute Change in Oyster Cover (%)"
  ) +
  scale_fill_manual(values = colors_treatment) +
  scale_y_continuous(breaks = seq(-15, 10, 5)) +
  theme_classic(base_size = 26) +
  theme(
    axis.title.y = element_text(
      size = 32,
      face = "bold",
      margin = margin(r = 20)
    ),
    axis.text.x = element_text(size = 24, color = "black"),
    axis.text.y = element_text(size = 24, color = "black"),
    strip.text = element_text(size = 24, face = "plain", color = "black"),
    strip.background = element_blank(),
    panel.spacing = unit(2, "cm"),
    plot.margin = margin(20, 20, 20, 40),
    legend.position = "none"
  )

# check fig
print(cover_change_fig)

# save
ggsave(
  filename = file.path("figs", "oyster_cover_change_fig.png"),
  plot = cover_change_fig,
  width = 17,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path("figs","oyster_cover_change_fig.pdf"),
  plot = cover_change_fig,
  width = 17,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)
```

#### Pit Count

```{r}
#| label: pit-count-figs

# prep data
pit_data <- exp_data_full %>%
  mutate(
    pit_count = replace_na(pit_count, 0),
    pit_cover_percent = replace_na(pit_cover_percent, 0),
    cover_level = factor(cover_level, levels = c("25", "50", "75", "100"))
  ) %>%
  filter(ray_access == "control")

summary(pit_data$pit_count)
table(pit_data$pit_count)
mean(pit_data$pit_count)
var(pit_data$pit_count)

# distribution 
ggplot(pit_data, aes(x = pit_count)) +
  geom_histogram(
    binwidth = 1,
    boundary = -0.5,
    color = "black",
    fill = "gray80"
  ) +
  labs(
    x = "Number of Pits",
    y = "Frequency"
  ) +
  theme_classic()

### MAY 26 PIT COUNT BASED ON INITIAL TREATMENT ###
# poisson glm
pit_count_glm <- glm(
  pit_count ~ cover_level,
  family = poisson,
  data = pit_data
)
dispersion <-
  sum(residuals(pit_count_glm, type = "pearson")^2) /
  df.residual(pit_count_glm)
dispersion

summary(pit_count_glm)
car::Anova(pit_count_glm, type = 2, test.statistic = "LR")

# summary stats
control_pits_summary <- pit_data %>%
  mutate(
    cover_level = factor(as.character(cover_level), levels = c("25", "50", "75", "100"))
  ) %>%
  group_by(cover_level) %>%
  summarise(
    n = n(),
    mean_pit_count = mean(pit_count, na.rm = TRUE),
    sd_pit_count = sd(pit_count, na.rm = TRUE),
    se_pit_count = sd_pit_count / sqrt(n),
    .groups = "drop"
  )

#fig colors
colors_pit <- c(
  "25" = "#007A87",
  "50" = "#6B8E23",
  "75" = "#D24A33",
  "100" = "#5A3E99"
)

#fig
pit_count_bar_fig <- ggplot(
  control_pits_summary,
  aes(x = cover_level, y = mean_pit_count, fill = cover_level)
) +
  geom_col(color = "black", linewidth = 0.8, width = 0.6) +
  geom_errorbar(
    aes(
      ymin = mean_pit_count - se_pit_count,
      ymax = mean_pit_count + se_pit_count
    ),
    width = 0.3,
    linewidth = 0.9
  ) +
  geom_jitter(
    data = pit_data,
    aes(x = cover_level, y = pit_count),
    inherit.aes = FALSE,
    width = 0.12,
    height = 0,
    size = 3.5,
    alpha = 0.6
  ) +
  labs(
    x = "Initial Oyster Cover (%)",
    y = "Number of Pits"
  ) +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
  scale_fill_manual(values = colors_pit) +
  theme_classic(base_size = 24) +
  theme(
    axis.title = element_text(size = 32, face = "bold"),
    axis.text = element_text(size = 24, color = "black"),
    plot.margin = margin(20, 20, 20, 40),
    legend.position = "none"
  )

pit_count_bar_fig

#save
ggsave(
  filename = file.path("figs", "pit_count_bar_fig.png"),
  plot = pit_count_bar_fig,
  width = 8,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)

#### MAY 26 OYS COVER + PIT COUNT LM ####

#linear model without initial cover level 
pit_count_lm <- lm(whole_oys_perc_cover ~ pit_count, data = pit_data)
summary(pit_count_lm)
anova(pit_count_lm)

### figure with pit_count_lm
pit_count_lm_fig <- ggplot(
  pit_data,
  aes(x = pit_count, y = whole_oys_perc_cover)
) +
  geom_point(
    shape = 21,
    size = 5.5,
    stroke = 1,
    color = "black",
    fill = "#e6b422",
    alpha = 0.6
  ) +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    color = "black",
    linewidth = 1.5,
    fill = "gray80"
  ) +
  labs(
    x = "Number of Pits",
    y = "Total Oyster Cover (%)"
  ) +
  scale_x_continuous(breaks = seq(0, 9, 1)) +
  scale_y_continuous(breaks = seq(0, 60, 10)) +
  coord_cartesian(xlim = c(0, 9), ylim = c(0, 60)) +
  theme_classic(base_size = 20) +
  theme(
    axis.title = element_text(size = 32, face = "bold"),
    axis.text = element_text(size = 24, color = "black"),
    plot.margin = margin(12, 12, 12, 12)
  )

print(pit_count_lm_fig)

ggsave(
  filename = file.path("figs", "pit_count_lm_fig.png"),
  plot = pit_count_lm_fig,
  width = 8,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)
```

##### Feedback after conference: 

#### Relative Oyster Cover Change

```{r}
{r}
#| label: relative-change-oyster-fig

# oyster change cover anova
anova_recovery <- aov(relative_delta_oyster_cover ~ cover_level * ray_access, data = exp_data_full)
print(summary(anova_recovery))

#check assumptions
plot(anova_recovery)


# figure colors
colors_treatment <- c(
  "25-Exclusion"    = "#A8D5E2",
  "25-Open"     = "#007A87",
  "50-Exclusion"    = "#CFE39A",
  "50-Open"     = "#6B8E23",
  "75-Exclusion"    = "#F4B39D",
  "75-Open"     = "#D24A33",
  "100-Exclusion"   = "#D4C2F0",
  "100-Open"    = "#5A3E99"
)

# prep data
cover_change_summary <- exp_data_full %>%
  group_by(cover_level, ray_access) %>%
  summarise(
    n = n(),
    mean_change = mean(relative_delta_oyster_cover, na.rm = TRUE),
    sd_change = sd(relative_delta_oyster_cover, na.rm = TRUE),
    se_change = sd_change / sqrt(n),
    .groups = 'drop'
  ) %>%
  mutate(
    ray_type = factor(ifelse(ray_access == "caged", "Exclusion", "Open"),
                      levels = c("Exclusion", "Open")),
    cover_level = factor(
      cover_level,
      levels = c("25", "50", "75", "100")
    ),
    color_key = paste0(cover_level, "-", ray_type)
  )

# plot
cover_change_fig <- ggplot(
  cover_change_summary,
  aes(x = ray_type, y = mean_change, fill = color_key)
) +
  geom_col(color = "black", width = 0.6, linewidth = 0.8) +
  geom_errorbar(
    aes(ymin = mean_change - se_change, ymax = mean_change + se_change),
    width = 0.3, 
    color = "black", 
    linewidth = 0.9
  ) +
  geom_hline(
    yintercept = 0, 
    linetype = "dashed", 
    color = "gray60", 
    linewidth = 0.7
  ) +
  facet_wrap(
    ~ cover_level, 
    nrow = 1,
    labeller = labeller(
      cover_level = c(
        "25" = "Initial 25% Cover",
        "50" = "Initial 50% Cover",
        "75" = "Initial 75% Cover",
        "100" = "Initial 100% Cover"
      )
    )
  ) +
  labs(
    x = "",
    y = "Relative Change in Oyster Cover (%)"
  ) +
  scale_fill_manual(values = colors_treatment) +
  scale_y_continuous(breaks = seq(-15, 10, 5)) +
  theme_classic(base_size = 26) +
  theme(
    axis.title.y = element_text(
      size = 32,
      face = "bold",
      margin = margin(r = 20)
    ),
    axis.text.x = element_text(size = 24, color = "black"),
    axis.text.y = element_text(size = 24, color = "black"),
    strip.text = element_text(size = 24, face = "plain", color = "black"),
    strip.background = element_blank(),
    panel.spacing = unit(2, "cm"),
    plot.margin = margin(20, 20, 20, 40),
    legend.position = "none"
  )

# check fig
print(cover_change_fig)

# save
ggsave(
  filename = file.path("figs", "relative_oyster_cover_change_fig.png"),
  plot = cover_change_fig,
  width = 17,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path("figs","relative_oyster_cover_change_fig.pdf"),
  plot = cover_change_fig,
  width = 17,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)
```
